Turbulence in compact to giant HII regions

### 2022-03-11 strucfunc_paper.tex
Start description of finite box effects

Combining both the effects of seeing and noise yields the corrected
model structure function:
\begin{multline}
  \tilde{B}
  \bigl( r; \ r_0, \sigma^2\pos, m, s_0, B_{\text{noise}} \bigr)
  = \\
  2\sigma^2\pos \left[
    1 - 2^{- \left( r/r_0 \right)^m} 
  \right]
  \,  S(r; s_0, r_0) + B_{\text{noise}}
\label{eq:sf-functional}
\end{multline}
An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.

The model that consider the effect of the observational box size is:

>>>>

Combining both the effects of seeing and noise yields the corrected
model structure function:
\begin{multline}
  \tilde{B}
  \bigl( r; \ r_0, \sigma^2\pos, m, s_0, B_{\text{noise}} \bigr)
  = \\
  2\sigma^2\pos \left[
    1 - 2^{- \left( r/r_0 \right)^m} 
  \right]
  \,  S(r; s_0, r_0) + B_{\text{noise}}
\label{eq:sf-functional}
\end{multline}
An example of this equation is shown by the red line in Figure~\ref{fig:model-strucfunc}.
Note that seeing and noise have opposite effects on the slope
of the structure function at intermediate scales:
seeing tends to steepen the slope, while noise tends to flatten it.
This can lead to a degeneracy between these two parameters
when fitting observations over a limited range of separations.

In Appendix~\ref{sec:finite-box-effects} we consider the effects
on the structure function of the finite size \(L\) of the observational map.
If the true correlation length \(r_0\) is more than a small fraction of the map size
(approximately, \(r_0 > 0.1 L\)),
then the apparent velocity variance \(\sigma^2'\) measured directly from the data
is less than the true \(\sigma^2\) of the underlying fluctuations
(see Figure~\ref{fig:finite-box-effect}).
This is because the observed map is not large enough to sample
the full range of velocity variations.
At the same time, the apparent correlation length \(r_0'\) is smaller
than the true value.

However, this does not mean that the model structure function needs to be modified;
equation
In the limit that \(r_0 \gg L\), then \(r_0'\) becomes independent of

finding that the apparent
